---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}
h2 {
  background-color: #f0f7ff;
  color: #2a4d69;
  padding: 6px 12px;
  border-left: 4px solid #4b86b4;
  border-radius: 4px;
  font-weight: 600;
}
```

## Exploring Daily Digital Habits

I spend a lot of time on my screens. For work, for fun, and honestly just out of habit. It’s not extreme, but it is one of those guilty pleasures where my phone is basically always with me. That got me wondering what the actual effects of this might be. That was the original motivation for the study, but once I started looking at the data, I realised the way I structured the form might shape the insights we get differently.

I asked people how they were feeling first, and only then about their screentime. In the plots below, you’ll see there isn’t much difference between lower, average, and higher screentime. It makes me wonder whether the results would look different if I’d asked the screentime question first.

For this analysis, I’m working with three variables: screentime (converted into minutes for consistency), mood_level (five levels), and screen_use (three categories).

```{r}
library(tidyverse)

# Csv link file not local, uploaded to web
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRY5PlCdZ8CWWPrADnSso0odpptJc16IxOV_7GSMxVy6osIMa2y8iqmXYOONNIEcgauU_fAaMt5K0XO/pub?gid=1317288649&single=true&output=csv")

latest_data <- logged_data %>%
  rename(mood_level = 2,
         screentime = 3, # HH:MM format
         screen_use = 4
         )

# Transform to char before numeric
latest_data$screentime <- as.character(latest_data$screentime) 

# Transform screentime to minutes for consistency
latest_data$screentime <- sapply(strsplit(latest_data$screentime, ":"), function(x) {
  as.numeric(x[1]) * 60 + as.numeric(x[2])
}) 

# Summaries
max_val <- latest_data$screentime %>%
  max() 

mean_val <- latest_data$screentime %>%
  mean()

min_val <- latest_data$screentime %>%
  min()

summary(latest_data$screentime)

paste("We have", max_val, "minutes as our highest screentime but overall we have", round(mean_val, 2), "minutes spent on screens")
```


```{r}
latest_data %>%
  ggplot() + 
  geom_bar(aes(x = mood_level,
               fill = screentime)) +
  labs(title = "Average Screentime with Mood Level",
       y = "Screentime (in minutes)",
       x = "Mood Level",
  )

latest_data %>%
  ggplot() + 
  geom_bar(aes(x = mood_level,
               fill = screen_use)) +
  labs(title = "Mood Level vs Screen Use",
       x = "Mood Level",
       y = "Screen Use",
  )
```

